Bone-Conduction Audio Interface to\\Guide People with Visual Impairments

### 2019-09-24 paper.tex
Made minor changes to coform to editor's requests

\usepackage{booktabs}
\usepackage[ruled]{algorithm2e} % For algorithms

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[caption=false]{subfig}
\usepackage[capitalise]{cleveref}
\usepackage{todonotes}

\usepackage{soul}
\DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}

@@

\author{Jacobus C. Lock\inst{1} \and 
Iain Gilchrist\inst{2} \and
Grzegorz Cielniak\inst{1} \and
Nicola Bellotto\inst{1}}

\institute{University of Lincoln \email{\{jlock, gcielniak, nbellotto\}@lincoln.ac.uk} \and
	   University of Bristol \email{i.d.gilchrist@bristol.ac.uk}}

\authorrunning{Jacobus C. Lock et.\ al.}

@@

\begin{abstract}
  The ActiVis\footnote{\url{https://lcas.github.io/ActiVis/}} project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
  To this end, we propose a new audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
  The vertical position on the median plan is given by adjusting the tone's pitch to overcome the audio localisation limitations of bone-conduction headphones. 
  This interface is validated through a set of experiments with blindfolded and visually impaired participants. 
\keywords{Human-machine interface \and vision impairment \and spatialised sound \and varying pitch \and bone-conduction}
\end{abstract}

@@

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
%The user's anatomy acts as a filter and the direction the sound wave hits the body activates different filter resonances, attenuating or accentuating different frequency bands.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous experimental results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2}, respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, all the participants in~\cite{stanley2006lateralization} had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for both groups are centred around the negative angle, as shown in \cref{fig:err-results}, indicating a possible underlying bias either in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization}. Further investigation with a larger participant pool is needed to determine this underlying bias, if any.

>>>>

\usepackage{booktabs}
\usepackage[ruled]{algorithm2e}

\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[caption=false]{subfig}
\usepackage[capitalise]{cleveref}

@@

\author{Jacobus C. Lock\inst{1} \and 
Iain D. Gilchrist\inst{2} \and
Grzegorz Cielniak\inst{1} \and
Nicola Bellotto\inst{1}}

\institute{University of Lincoln, Lincoln, LN6 7TS, UK \email{\{jlock, gcielniak, nbellotto\}@lincoln.ac.uk} \and
	   University of Bristol, Bristol, BS8 1TH, UK \email{i.d.gilchrist@bristol.ac.uk}}

\authorrunning{Jacobus C. Lock et.\ al.}
\titlerunning{Bone-conduction Interface For People with Visual Impairments}

@@

\begin{abstract}
  The ActiVis project's aim is to build a mobile guidance aid to help people with limited vision find objects in an unknown environment.
  This system uses bone-conduction headphones to transmit audio signals to the user and requires an effective non-visual interface.
  To this end, we propose a new audio-based interface that uses a spatialised signal to convey a target's position on the horizontal plane. 
  The vertical position on the median plan is given by adjusting the tone's pitch to overcome the audio localisation limitations of bone-conduction headphones. 
  This interface is validated through a set of experiments with blindfolded and visually impaired participants. 
\keywords{Human-machine interface \and vision impairment \and spatialised sound \and varying pitch \and bone-conduction}
\end{abstract}

@@

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous experimental results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.25}{\radian} and \SI{0.36}{\radian} for groups \textit{G1} and \textit{G2}, respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 63\% and 47\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a more modest improvement of 43\% in \textit{G1} and 16\% for \textit{G2} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization}.
However, all the participants in~\cite{stanley2006lateralization} had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for both groups are centred around the negative angle, as shown in \cref{fig:err-results}, indicating a possible underlying bias either in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization}. Further investigation with a larger participant pool is needed to determine this underlying bias, if any.
